\usepackage{graphicx}



%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01

\documentclass[preprint,12pt, a4paper]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
\usepackage{lineno}

\usepackage{float}
\restylefloat{table}

\journal{SoftwareX}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Original Software Publication: A workflow process on storing sources according to commonalities}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author{Ellen Kirkpatrick}

\address{Macquarie University, Sydney Australia}

\begin{abstract}
%% Text of abstract 
This original software publication (OSP) provides the necessary details for the most efficient process of storing data according to its relevance or commonalities with other sources so it can be easily referred to at later stages in the research process. This will ensure that information collected at the beginning of the research process is not lost and other collaborators can easily identify and find sources. The softwares involved are Voyant tools (via web browser) and Zotero. 

\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Sources \sep Commonalities \sep Storage \sep Grouping \sep Voyant \sep Zotero

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

\section*{Required Metadata}
\label{}

\section*{Current code version}
\label{}
%%Ancillary data table required for subversion of the codebase. Kindly replace examples in right column with the correct information about your current code, and leave the left column as it is.
\begin{table}[H]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this column} \\
\hline
C1 & Current code version & v1.0 \\
\hline
C2 & Permanent link to code/repository used for this code version &  $https://github.com/MQ-FOAR705/E-Kirkpatrick-PoC-project \\
\hline
C3 & Code Ocean compute capsule & For example: $https://codeocean.com/2017/07/30/neurospeech-colon-an-open-source-software-for-parkinson-apos-s-speech-analysis/code$\\
\hline
C4 & Legal Code License   & GPL-v3.0 \\
\hline
C5 & Code versioning system used & Voyant Tools (via web browser), Zotero \\
\hline
C6 & Software code languages, tools, and services used & No coding language in addition to internal coding performed by programs - Voyant and Zotero (javascript) \\
\hline
C7 & Compilation requirements, operating environments \& dependencies & User stories: finding and downloading sources, and identifying commonalities are essential. Other user stories dependent on success of these. User stories must be followed in order for maximum efficiency. Operation can be performed on any computer with access to internet and sufficient space for Zotero installation.  \\
\hline
C8 & If available Link to developer documentation/manual & $https://github.com/MQ-FOAR705/E-Kirkpatrick-POC-Implementation-and-instructions \\
\hline
C9 & Support email for questions & ellen.kirkpatrick@students.mq.edu.au\\
\hline
\end{tabular}
\caption{Metadata for project}
\label{} 
\end{table}


\linenumbers

%% main text

%%The permanent link to code/repository or the zip archive should include the following requirements: 

%%README.txt and LICENSE.txt.

%%Source code in a src/ directory, not the root of the repository.

%%Tag corresponding with the version of the software that is reviewed.

%%Documentation in the repository in a docs/ directory, and/or READMEs, as appropriate.

\section{Motivation and significance}
\label{}

%%Introduce the scientific background and the motivation for developing the software.
%%Explain why the software is important, and describe the exact (scientific) problem(s) it solves.
%%Indicate in what way the software has contributed (or how it will contribute in the future) to the process of scientific discovery; if available, this is to be supported by citing a research paper using the software.

Many disciplines within the social sciences, draw on the use of multiple sources when conducting research. Often this includes many peer-reviewed journal articles or other scholarly sources from a range of databases that are being used for specific sections of the research, and at times, this can become confusing. It can also become problematic, especially in later stages of research, when researchers are required to refer to sources from earlier stages, or collaborate with others on a project. This may have a detrimental impact on the research process if researchers cannot remember the location of a source or its relevance.\\
Thus, this project is motivated by the intention to improve this research process in order to make it more efficient. By demonstrating a workflow process through which sources can be directly saved from online databases to a storage program, and shared themes, terms and othe commonalities identified; it is possible to group and annotate sources accordingly so that they can be searched and accessed in the future more efficiently. This also makes coordination between collaborators easier as each researcher can identify why the source has been selected and where it fits in throughout the entire research process. It also makes publication easier with metadata being attached to sources in the storage program which allows for bibliographic details and citations to be transferred to publishing programs. \\
This is important for students, academics or researchers as it makes the research process and publishing process more time beneficial and efficient. Sources do not have to be repeatedly searched for and all information can be kept in the same place.
\subsection{Experimental Setting}
%%Provide a description of the experimental setting (how does the user use the software?).
%%Introduce related work in literature (cite or list algorithms used, other software etc.).

\section{Software description}
\label{}
%%Describe the software in as much as is necessary to establish a vocabulary needed to explain its impact. 
This project documents a workflow process through which sources can be saved directly, along with the appropriate metadata, from an online database into a local storage program. From there, they can be transferred into another online platform to identify any shared themes, terms or other commonalities between them which allows the sources to be annotated accordingly and grouped together for further research. This is useful for students, academics or researchers who are conducting large research projects and need to use large amounts of sources from different databases. It aims to reduce stress and create benefits in later stages of the research process where sources need to be re-accessed and the metadata transferred for researching publishing. 

\subsection{Software Architecture}
\label{}
%%Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.
\subsubsection{Voyant}

\subsubsection{Zotero}
Zotero is an open-source reference management software. It can store sources and related metadata together so they can be accessed together at any point of time. It is useful for managing bibliographic and reference details. It can integrate with publishing programs including Microsoft Word to transfer bibliographic details and citations. It uses javascript as a programming language.\\
Zotero is available on macOS (10.11 or later), Windows (7 or later) and Linux. Zotero is released under the General Public License (version 3).\\
To optimise efficiency, it is best to install the plugins and connectors for Zotero. For instance, a browser connector allows sources to be saved quickly. Word processor plugins are also available to generate citations.

\subsection{Software Functionalities}
\label{}
%%Present the major functionalities of the software.
\subsubsection{Voyant}
\subsubsection{Zotero}
\subsubsection{Workflow Process}
- putting it all together, to see how they can be used together to finish a goal.


\subsection{Sample code snippets analysis (optional)}
\label{}

\section{Illustrative Examples}
\label{}

Provide at least one illustrative example to demonstrate the major functions.


\section{Impact}
\label{}

\textbf{This is the main section of the article and the reviewers weight the description here appropriately}

%%Indicate in what way new research questions can be pursued as a result of the software (if any).
Can move further with this workflow process to automate the process, or discover other programs which can complete similar goals but may be more suitable to different study and research styles. Further time could prove useful.
%%Indicate in what way, and to what extent, the pursuit of existing research questions is improved (if so).
Have been improved as it is now easier to identify how sources relate to each other and can identify that from the very start of the research process. Also makes storing more efficient as instead of printing out or having multiple repositries for different sources. It has improved how sources can be stored and accessed in future without losing their relevance or their place in the research process.
%%Indicate in what way the software has changed the daily practice of its users (if so).
Being introduced to these programs has been very important as it has made users release what softwares/programs are available, how they can be utilised throughout the study process in the future.
%%Indicate how widespread the use of the software is within and outside the intended user group.
%%Indicate in what way the software is used in commercial settings and/or how it led to the creation of spin-off companies (if so).

\section{Conclusions}
\label{}

Set out the conclusion of this original software publication.

\section{Conflict of Interest}
Please select the appropriate text:

Potential conflict of interest exists:
We wish to draw the attention of the Editor to the following facts, which may be considered as potential conflicts of interest, and to significant financial contributions to this work. The nature of potential conflict of interest is described below: [Describe conflict of interest]

No conflict of interest exists:
We wish to confirm that there are no known conflicts of interest associated with this publication and there has been no significant financial support for this work that could have influenced its outcome.


\section*{Acknowledgements}
\label{}
%%Optionally thank people and institutes you need to acknowledge. 
I would like to personally thank Brian Ballsun-Stanton, Shawn Ross and Kathryn Elliot from the teaching staff of FOAR705 at Macquarie University for their tireless efforts and patience throughout the development of this workflow process over the course of 13 weeks. Without them, progress would never have been possible. Although there is still a long way to go, they have been very helpful in introducing new methods, softwares, programs and approaches to research which I didn't know existed previously to beginning this project and I would like to thank them for opening up many new avenues and directions to explore in the future when conducting research.

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% References:
%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
%%  \bibliographystyle{elsarticle-num} 
%%  \bibliography{<your bibdatabase>}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

\begin{thebibliography}{00}


%% \bibitem{label}
%% Text of bibliographic item

\bibitem{}
https://github.com/MQ-FOAR705/E-Kirkpatrick-PoC-project\\
This provides the project management, licence, version and user stories for this workflow process.\\
\bibitem{}
https://github.com/MQ-FOAR705/E-Kirkpatrick-POC-Implementation-and-instructions\\
This provides the documentation for this research process.\\
\bibitem{}
https://github.com/MQ-FOAR705/OSP---E-Kirkpatrick\\
This provides the soft copy of this publication. 
\end{thebibliography}
%%Please add the reference to the software repository if DOI for software  is available. 


\section*{Current executable software version}
\label{}
%%Ancillary data table required for sub version of the executable software: (x.1, x.2 etc.) kindly replace examples in right column with the correct information about your executables, and leave the left column as it is.

\begin{table}[!h]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{(Executable) software metadata description} & \textbf{Please fill in this column} \\
\hline
S1 & Current software version & For example 1.1, 2.4 etc. \\
\hline
S2 & Permanent link to executables of this version  & For example: $https://github.com/combogenomics/$ $DuctApe/releases/tag/DuctApe-0.16.4$ \\
\hline
S3 & Legal Software License & List one of the approved licenses \\
\hline
S4 & Computing platforms/Operating Systems & For example Android, BSD, iOS, Linux, OS X, Microsoft Windows, Unix-like , IBM z/OS, distributed/web based etc. \\
\hline
S5 & Installation requirements \& dependencies & \\
\hline
S6 & If available, link to user manual - if formally published include a reference to the publication in the reference list & For example: $http://mozart.github.io/documentation/$ \\
\hline
S7 & Support email for questions & \\
\hline
\end{tabular}
\caption{Software metadata (optional)}
\label{} 
\end{table}

\end{document}
\endinput
%%
%% End of file `SoftwareX_article_template.tex'.
